Weak Lensing Shear Inference:A Hierarchy Bayesian Approach

### 2013-02-18 write-up.tex
updte write-up.tex

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

@@

The Jacobi term $|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|$
and Beta function $Beta(p,q)$ are calculated numerically.

@@

>>>>

%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{luainputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{esint}

@@

The Jacobean term $|\frac{\partial(x_{0},y_{0})}{\partial(x_{\ell},y_{\ell})}|$
and Beta function $Beta(p,q)$ are calculated numerically.

@@

Figure 10 shows how the mean square error of the Hierarchy Bayesian
method varies with the number of sky patches used,in comparison with
traditional average method and likelihood analysis with correct P($\epsilon$)
hard-set.from this figure we can see that the mean square error of
the Hierarchy Bayesian method decreases as the number of patches goes
up,while this trend is less significant as number of patches becomes
larger.Moreover,down to 8 patches this Hierarchy Bayesian method still
out perform the traditional average method. Meanwhile the likelihood
analysis with correct P($\epsilon$) shows higher accuracy than Hierarchy
Bayesian method. That is consistent with our speculation. When the
number of patches goes to infinity ,we will have correct estimation
on P($\epsilon$) and Hierarchy Bayesian method converges to likelihood
analysis with correct $P(\epsilon)$ hard-set,ignoring the difference
between our step function model and real beta function,of course.

\includegraphics[scale=0.5]{Np_step}

\includegraphics[scale=0.5]{N16NP_vary}

Figure 10:Mean square error VS Number of patches.In the upper graph
number of galaxies per patch is 8 while in the lowwer it's 16.The
Green line is mean square error of traditional average while the red
line is that of likelihood analysis with correct $P(\epsilon)$ .

\subsection{Shape Measurement Error}

In this part we will discuss how the shape measurement error will
affect the relative accuracy of this Hierarchy Bayesian method.As
mentioned before ,we try to avoid any image process which is another
important aspect of Weak Lensing survey ,so we simply assume a 2D
Gaussian noise on ellipticity measurement.

With that Gaussian noise the data we can obtain becomes the observed
ellipticity $\epsilon_{ob}$,whoes probability distribution is 
\begin{equation}
f(\epsilon_{ob}|\epsilon_{\ell})\varpropto e^{-\frac{(\epsilon_{ob}-\epsilon_{\ell})^{2}}{2\sigma^{2}}}
\end{equation}

Therefore the likelihood of $g$ and $\alpha$ becomes
\begin{equation}
L(g,\alpha|\epsilon_{ob})=P(\epsilon_{ob}|g,\alpha)=\intop f(\epsilon_{ob}|\epsilon_{\ell})P(\epsilon_{\ell}|g,\alpha)d\epsilon_{\ell}
\end{equation}
